Local-to-Global Mariculture Modelling

### 2025-12-18 docs-working/08_data_analysis.qmd
Updates to docs

---
title: "Process data from Atlantic salmon model runs"
format: html
editor: source
---

@@

here("src") %>% 
  list.files(pattern = "\\.R$", full.names = TRUE) %>% 
  str_subset("map", negate = T) %>% 
  walk(source)

@@

```{r raw-outputs}
total_ends <- qread(file.path(output_model_farm_path, "total_ends.qs")) %>% 
  mutate(
    feed_group = as.factor(str_remove(feed, "_min|_max")),
    feed_type = case_when(
      str_detect(feed, "_min") ~ "min",
      str_detect(feed, "_max") ~ "max",
      T ~ "mean"
    ) %>% as.factor(),
    mean = set_units(mean, "g"),
    sd = set_units(sd, "g"),
    mean_biomass = set_units(mean, "g g_fish-1"),
    sd_biomass = set_units(sd, "g g_fish-1")
  )

cohort_results <- qread(file.path(output_model_cohort_path, "cohort_results.qs")) %>% 
  mutate(
    feed_group = as.factor(str_remove(feed, "_min|_max")),
    feed_type = case_when(
      str_detect(feed, "_min") ~ "min",
      str_detect(feed, "_max") ~ "max",
      T ~ "mean"
    ) %>% as.factor()
  )
```

# Feed provided and lost

```{r feed-prov-lost}
#| code-summary: Show differences between diets in feed provided and lost
#| fig-cap: Mean food provided and uneaten feed lost to the environment (g/g salmon)

feed_end <- total_ends %>% 
  filter(measure %in% c("total_uneat_stat", "food_prov_stat")) %>% 
  mutate(measure = droplevels(measure))

ggplot(
    feed_end, 
    aes(x = feed_group, y = mean_per_biom, fill = feed_type, group = feed)
  ) +
  geom_boxplot() +
  facet_wrap(facets = vars(measure), scales = "free") +
  prettyplot_300()
```

# Faeces excreted

```{r feed-prov-lost}
#| code-summary: Show differences between diets in feed provided and lost

feed_end <- total_ends %>% 
  filter(measure %in% c("total_uneat_stat", "food_prov_stat")) %>% 
  mutate(measure = droplevels(measure))

ggplot(
    feed_end, 
    aes(x = feed_group, y = mean_per_biom, fill = feed_type, group = feed)
  ) +
  geom_boxplot() +
  facet_wrap(facets = vars(measure), scales = "free") +
  prettyplot_300()
```

# Total waste

# Raw output processing

For some of the outputs of the model, it makes sense to sum them across a production period and/or calculate their values per unit of biomass. 
```{r}
#| label: biomass-location-globals-farm

farm_locs <- find_read(output_farm_data_path, "geometry") %>% 
  rename(farm_ID = farm_id) %>% 
  mutate(country = as.factor(country))

fish_weight <- find_read(output_model_farm_path, "weight")
farm_biomass <- find_read(output_model_farm_path, "biomass_stat")
biomass_produced <- find_read(output_model_farm_path, "biomass_produced")

# farm_biomass has had the final day (when fish are not fed) removed - this adds it back
all_biomass <- rbind(farm_biomass, biomass_produced)
qs::qsave(all_biomass, file.path(data_analysis_path, "all_biomass.qs"))

farm_biomass %>% filter(farm_ID == 1) %>% pull(t) %>% unique() %>% length()
all_biomass %>% filter(farm_ID == 1) %>% pull(t) %>% unique() %>% length()
```

@@

```{r}
#| label: summed-per-biomass-outputs

@@

```{r}
#| label: biomass-location-globals-cohort

@@

```{r}
#| label: summed-per-biomass-outputs-cohort
#| eval: false

@@

```{r}
#| label: biomass-produced-comparisons

@@

```{r}
#| label: food-provided-comparison

@@

```{r}
#| label: uneaten-feed-comparisons

@@

## Does excretion increase or decrease with novel feeds?

```{r}
#| label: excreted-comparison

# Summed across the whole production period
total_excr_farm_summed <- find_read(data_analysis_path, "total_excr_farm_summed") %>% 
  st_drop_geometry() %>% 
  mutate(
    feed = factor(
      feed, 
      levels = c("marine_dominant", "plant_dominant", "novel_inclusive"),
      labels = c("MD", "PD", "NI")
    )
  ) %>% 
  pivot_wider(
    names_from = feed,
    values_from = c(total, sd), values_fn = list(total = drop_units, sd = drop_units),
    id_cols = c(country, farm_ID, measure, days)
  ) %>% 
  mutate(
    sd_MD = (1/total_PD) * sqrt(sd_MD^2 + sd_PD^2),
    sd_NI = (1/total_PD) * sqrt(sd_NI^2 + sd_PD^2),
    total_MD = (total_MD-total_PD)/total_PD,
    total_NI = (total_NI-total_PD)/total_PD
  ) %>% 
  select(-contains("PD")) %>% 
  pivot_longer(
    names_to = c(".value", "feed"), names_sep = "_", names_transform = list(feed = as.factor),
    cols = contains(c("sd", "total"))
  ) %>% 
  merge(farm_locs, by = c("country", "farm_ID")) %>% 
  st_as_sf()

# Check that it looks reasonable
# ggplot(total_excr_farm_summed, aes(x = country, y = total, fill = feed)) +
#   geom_boxplot()

qs::qsave(total_excr_farm_summed, file.path(comparisons_path, "total_excr_farm_summed.qs"))
rm(total_excr_farm_summed)

# Summed across the whole production period, per biomass of fish produced
total_excr_farm_per_biom_summed <- find_read(data_analysis_path, "total_excr_farm_per_biom_summed") %>% 
  st_drop_geometry() %>% 
  mutate(
    feed = factor(
      feed, 
      levels = c("marine_dominant", "plant_dominant", "novel_inclusive"),
      labels = c("MD", "PD", "NI")
    )
  ) %>% 
  pivot_wider(
    names_from = feed, names_sep = ".", 
    values_from = c(mean_biom, sd_biom), values_fn = list(mean_biom = drop_units, sd_biom = drop_units),
    id_cols = c(country, farm_ID, measure)
  ) %>% 
  mutate(
    sd_biom.MD = (1/mean_biom.PD) * sqrt(sd_biom.PD^2 + sd_biom.MD^2),
    sd_biom.NI = (1/mean_biom.PD) * sqrt(sd_biom.PD^2 + sd_biom.NI^2),
    mean_biom.MD = (mean_biom.MD-mean_biom.PD)/mean_biom.PD,
    mean_biom.NI = (mean_biom.NI-mean_biom.PD)/mean_biom.PD
  ) %>% 
  select(-contains("PD")) %>% 
  pivot_longer(
    names_to = c(".value", "feed"), names_sep = "[.]", names_transform = list(feed = as.factor),
    cols = contains(c("sd_biom", "mean_biom"))
  ) %>% 
  merge(farm_locs, by = c("country", "farm_ID")) %>% 
  st_as_sf()

# Check that it looks reasonable
# ggplot(total_excr_farm_per_biom_summed, aes(x = country, y = mean_biom, fill = feed)) +
#   geom_boxplot()

qs::qsave(total_excr_farm_per_biom_summed, file.path(comparisons_path, "total_excr_farm_per_biom_summed.qs"))
rm(total_excr_farm_per_biom_summed)
```

## Do total inputs (mass, excreted and uneaten) increase or decrease with novel feeds?

```{r}
#| label: total-mass-inputs-comparison

total_mass_inputs_farm_summed <- rbind(
  find_read(data_analysis_path, "total_uneat_farm_summed"), 
  find_read(data_analysis_path, "total_excr_farm_summed")
) %>% 
  st_drop_geometry() %>% 
  mutate(
    feed = factor(
      feed, 
      levels = c("marine_dominant", "plant_dominant", "novel_inclusive"),
      labels = c("MD", "PD", "NI")
    )
  ) %>% 
  group_by(country, farm_ID, feed, days) %>% 
  reframe(
    total = sum(total),
    sd = sqrt(sum(sd^2)),
    measure = as.factor("excr_uneat")
  )
qs::qsave(total_mass_inputs_farm_summed, file.path(data_analysis_path, "total_mass_inputs_farm_summed.qs"))
rm(total_mass_inputs_farm_summed)

# Summed across the whole production period
total_mass_inputs_farm_summed <- rbind(
  find_read(data_analysis_path, "total_uneat_farm_summed"), 
  find_read(data_analysis_path, "total_excr_farm_summed")
) %>% 
  st_drop_geometry() %>% 
  mutate(
    feed = factor(
      feed, 
      levels = c("marine_dominant", "plant_dominant", "novel_inclusive"),
      labels = c("MD", "PD", "NI")
    )
  ) %>% 
  group_by(country, farm_ID, feed, days) %>% 
  reframe(
    total = sum(total),
    sd = sqrt(sum(sd^2)),
    measure = as.factor("excr_uneat")
  ) %>% 
  pivot_wider(
    names_from = feed,
    values_from = c(total, sd), values_fn = list(total = drop_units, sd = drop_units),
    id_cols = c(country, farm_ID, measure, days)
  ) %>% 
  mutate(
    sd_MD = (1/total_PD) * sqrt(sd_MD^2 + sd_PD^2),
    sd_NI = (1/total_PD) * sqrt(sd_NI^2 + sd_PD^2),
    total_MD = (total_MD-total_PD)/total_PD,
    total_NI = (total_NI-total_PD)/total_PD
  ) %>% 
  select(-contains("PD")) %>% 
  pivot_longer(
    names_to = c(".value", "feed"), names_sep = "_", names_transform = list(feed = as.factor),
    cols = contains(c("sd", "total"))
  ) %>% 
  merge(farm_locs, by = c("country", "farm_ID")) %>% 
  st_as_sf()

# Check that it looks reasonable
ggplot(total_mass_inputs_farm_summed, aes(x = country, y = total, fill = feed)) +
  geom_boxplot()

qs::qsave(total_mass_inputs_farm_summed, file.path(comparisons_path, "total_mass_inputs_farm_summed.qs"))
rm(total_mass_inputs_farm_summed)

# Summed across the whole production period, per biomass of fish produced
total_mass_inputs_farm_per_biom_summed <- rbind(
  find_read(data_analysis_path, "total_uneat_farm_per_biom_summed"), 
  find_read(data_analysis_path, "total_excr_farm_per_biom_summed")
  ) %>% 
  st_drop_geometry() %>% 
  mutate(
    feed = factor(
      feed, 
      levels = c("marine_dominant", "plant_dominant", "novel_inclusive"),
      labels = c("MD", "PD", "NI")
    )
  ) %>% 
  group_by(country, farm_ID, feed) %>% 
  reframe(
    mean_biom = sum(mean_biom),
    sd_biom = sqrt(sum(sd_biom^2)),
    measure = as.factor("excr_uneat")
  ) %>% 
  pivot_wider(
    names_from = feed, names_sep = ".", 
    values_from = c(mean_biom, sd_biom), values_fn = list(mean_biom = drop_units, sd_biom = drop_units),
    id_cols = c(country, farm_ID, measure)
  ) %>% 
  mutate(
    sd_biom.MD = (1/mean_biom.PD) * sqrt(sd_biom.PD^2 + sd_biom.MD^2),
    sd_biom.NI = (1/mean_biom.PD) * sqrt(sd_biom.PD^2 + sd_biom.NI^2),
    mean_biom.MD = (mean_biom.MD-mean_biom.PD)/mean_biom.PD,
    mean_biom.NI = (mean_biom.NI-mean_biom.PD)/mean_biom.PD
  ) %>% 
  select(-contains("PD")) %>% 
  pivot_longer(
    names_to = c(".value", "feed"), names_sep = "[.]", names_transform = list(feed = as.factor),
    cols = contains(c("sd_biom", "mean_biom"))
  ) %>% 
  merge(farm_locs, by = c("country", "farm_ID")) %>% 
  st_as_sf()

# Check that it looks reasonable
ggplot(total_mass_inputs_farm_per_biom_summed, aes(x = country, y = mean_biom, fill = feed)) +
  geom_boxplot()

qs::qsave(total_mass_inputs_farm_per_biom_summed, file.path(comparisons_path, "total_mass_inputs_farm_per_biom_summed.qs"))
rm(total_mass_inputs_farm_per_biom_summed)
```

## Does the proportion of total inputs (mass) attributed to excretion increase or decrease with novel feeds?

```{r}
#| label: proportion-of-waste-comparison

proportion_of_waste <- find_read(data_analysis_path, "total_excr_farm_summed") %>% 
  st_drop_geometry() %>% 
  mutate(
    feed = factor(
      feed, 
      levels = c("marine_dominant", "plant_dominant", "novel_inclusive"),
      labels = c("MD", "PD", "NI")
    )
  ) %>% 
  rbind(find_read(data_analysis_path, "total_mass_inputs_farm_summed.qs")) %>% 
  mutate(
    measure = factor(
      measure, 
      levels = c("total_excr_stat", "excr_uneat"),
      labels = c("excr", "waste")
      )
  ) %>% 
  pivot_wider(
    names_from = measure,
    values_from = c(total, sd), values_fn = list(total = drop_units, sd = drop_units),
    id_cols = c(country, farm_ID, feed, days)
  ) %>% 
  mutate(
    total = total_excr/total_waste,
    sd = (total_excr/total_waste) * sqrt((sd_waste/total_waste)^2 + (sd_excr/total_excr)^2)
  ) %>% 
  select(-contains(c("waste", "excr")))

# Check that it looks reasonable
ggplot(proportion_of_waste, aes(x = country, y = total, fill = feed)) +
  geom_boxplot()

qs::qsave(proportion_of_waste, file.path(comparisons_path, "excr_proportion_of_waste.qs"))
rm(proportion_of_waste)
```

@@

```{r}
#| label: PLC-mass-inputs-comparison

@@

```{r}
#| label: macronutrient-proportion-comparison

@@

```{r}
#| label: uneaten-feed-N-comparison

@@

```{r}
#| label: excreted-N-comparison

@@

```{r}
#| label: total-N-comparison

@@

```{r}

@@

```{r}

```

>>>>

---
title: "Process data from Atlantic salmon model runs"
author: "Tormey Reimer"
date: today
---

@@

here("src") %>% 
  list.files(pattern = "\\.R$", full.names = TRUE) %>% 
  walk(source)

@@

```{r raw-outputs}
total_ends <- file.path(output_model_farm_path, "total_ends.qs") %>% 
  qread() %>% 
  mutate(
    feed_group = factor(
      str_remove(feed, "_min|_max"), 
      levels = long_feeds,
      labels = short_feeds
      ),
    feed_type = case_when(
      str_detect(feed, "_min") ~ "min",
      str_detect(feed, "_max") ~ "max",
      T ~ "mean"
      ) %>% as.factor(),
    mean = set_units(mean, "g"),
    sd = set_units(sd, "g"),
    mean_biomass = set_units(mean_biomass, "g_fish"),
    sd_biomass = set_units(sd_biomass, "g_fish"),
    mean_per_biom = set_units(mean_per_biom, "g g_fish-1"),
    sd_per_biom = set_units(sd_per_biom, "g g_fish-1")
  )

cohort_results <- file.path(output_model_cohort_path, "cohort_results.qs") %>% 
  qread() %>% 
  mutate(
    feed_group = factor(
      str_remove(feed, "_min|_max"), 
      levels = long_feeds,
      labels = short_feeds
      ),
    feed_type = case_when(
      str_detect(feed, "_min") ~ "min",
      str_detect(feed, "_max") ~ "max",
      T ~ "mean"
      ) %>% as.factor(),
    mean = set_units(mean, "g"),
    sd = set_units(sd, "g"),
    mean_biomass = set_units(mean_biomass, "g_fish"),
    sd_biomass = set_units(sd_biomass, "g_fish"),
    mean_per_biom = set_units(mean_per_biom, "g g_fish-1"),
    sd_per_biom = set_units(sd_per_biom, "g g_fish-1")
  )
```

```{r basic-stats}
#| code-summary: Code to generate plot
#| fig-height: 12

total_ends %>% 
  filter(!measure %in% c("biomass_stat", "food_prov_stat")) %>% 
  mutate(
    measure = factor(measure, levels = c(
      "C_excr_stat", "C_uneat_stat", 
      "L_excr_stat", "L_uneat_stat", 
      "P_excr_stat", "P_uneat_stat", 
      "total_excr_stat", "total_uneat_stat"
    )),
    mean_per_biom = set_units(mean_per_biom, "g kg_fish-1")
  ) %>% 
  ggplot(aes(x = feed_group, y = mean_per_biom, fill = feed_type)) +
  geom_boxplot() +
  facet_wrap(facets = vars(measure), scales = "free", ncol = 2) +
  prettyplot_600() +
  theme(legend.position = "right")

# | Description | Plant-dominant | Marine-dominant | Novel-inclusive | Change from PD to MD (%) | Change from PD to NI (%) |
# |:--------------------------|:----------:|:----------:|:----------:|:----------:|:----------:|
# | Salmon biomass produced (t)                         | `r bpr1$PD`        | `r bpr1$MD`        | `r bpr1$NI`        | `r coln(bpr2$MD)`    | `r coln(bpr2$NI)`    |
# | Feed provided (t)                                   | `r fpr1$PD`        | `r fpr1$MD`        | `r fpr1$NI`        | `r coln(fpr2$MD)`    | `r coln(fpr2$NI)`    |
# | Feed provided (kg/kg salmon)                        | `r fpr_pb1$PD`     | `r fpr_pb1$MD`     | `r fpr_pb1$NI`     | `r coln(fpr_pb2$MD)` | `r coln(fpr_pb2$NI)` |
# | Uneaten feed (t)                                    | `r tuf1$PD`        | `r tuf1$MD`        | `r tuf1$NI`        | `r coln(tuf2$MD)`    | `r coln(tuf2$NI)`    |
# | Excreted waste (t)                                  | `r tew1$PD`        | `r tew1$MD`        | `r tew1$NI`        | `r coln(tew2$MD)`    | `r coln(tew2$NI)`    |
# | Total waste (E+U, t)                                | `r tow1$PD`        | `r tow1$MD`        | `r tow1$NI`        | `r coln(tow2$MD)`    | `r coln(tow2$NI)`    |
# | Proportion of total waste composed of excretion (%) | `r epw$PD`         | `r epw$MD`         | `r epw$NI`         |                      |                      |
# | Total protein waste (t)                             | `r sum(plc1$PD_P)` | `r sum(plc1$MD_P)` | `r sum(plc1$NI_P)` | `r coln(plc3$MD_P)`  | `r coln(plc3$NI_P)`  |
# | Total carbohydrate waste (t)                        | `r sum(plc1$PD_C)` | `r sum(plc1$MD_C)` | `r sum(plc1$NI_C)` | `r coln(plc3$MD_C)`  | `r coln(plc3$NI_C)`  |
# | Total lipid waste (t)                               | `r sum(plc1$PD_L)` | `r sum(plc1$MD_L)` | `r sum(plc1$NI_L)` | `r coln(plc3$MD_L)`  | `r coln(plc3$NI_L)`  |
# | Proportion of protein waste from excretion (%)      | `r plc2$PD_P`      | `r plc2$MD_P`      | `r plc2$NI_P`      |                      |                      |
# | Proportion of carbohydrate waste from excretion (%) | `r plc2$PD_C`      | `r plc2$MD_C`      | `r plc2$NI_C`      |                      |                      |
# | Proportion of lipid waste from excretion (%)        | `r plc2$PD_L`      | `r plc2$MD_L`      | `r plc2$NI_L`      |                      |                      |
# | Total N from uneaten feed (t)                       | `r niu1$PD`        | `r niu1$MD`        | `r niu1$NI`        | `r coln(niu2$MD)`    | `r coln(niu2$NI)`    |
# | Total N from excreted waste (t)                     | `r nie1$PD`        | `r nie1$MD`        | `r nie1$NI`        | `r coln(nie2$MD)`    | `r coln(nie2$NI)`    |
# | Total N inputs (E+U, t)                             | `r nit1$PD`        | `r nit1$MD`        | `r nit1$NI`        | `r coln(nit2$MD)`    | `r coln(nit2$NI)`    |
# : Summary of all results. Unless otherwise specified, values presented are means across all farms, summed across a single production period. In the % change columns, the colour of the text indicates whether there is an increase (red) or a decrease (green). Some cells of this table are blank - sometimes that means it doesn't make sense to fill that cell, but sometimes it means I haven't got to it yet. {#tbl-results-summary}
```

## Feed provided and lost

```{r feed-prov-lost}
#| code-summary: Code to generate plot
#| fig-cap: Mean food provided and uneaten feed lost to the environment when feeds use minimum (blue), maximum (red) or mean (green) digestibility coefficients.

feed_end <- total_ends %>% 
  filter(measure %in% c("total_uneat_stat", "food_prov_stat"))

feed_end %>% 
  mutate(
    mean_per_biom = set_units(mean_per_biom, "g kg_fish-1"),
    measure = droplevels(measure)
    ) %>% 
  ggplot(aes(x = feed_group, y = mean_per_biom, fill = feed_type, group = feed)) +
  geom_boxplot() +
  facet_wrap(facets = vars(measure), scales = "free") +
  prettyplot_300()
```

## Faeces excreted and proportion of total waste

```{r faeces-excreted}
#| code-summary: Code to generate plot
#| fig-cap: Mean faeces excreted and proportion of total waste coming from faeces when feeds use minimum (blue), maximum (red) or mean (green) digestibility coefficients.

faeces_end <- total_ends %>% 
  filter(measure %in% c("total_excr_stat", "total_uneat_stat")) %>% 
  select(farm_ID, feed, feed_type, feed_group, measure, mean_per_biom) %>% 
  mutate(
    mean_per_biom = set_units(mean_per_biom, "g kg_fish-1") %>% drop_units(),
    measure = droplevels(measure)
    ) %>%
  pivot_wider(
    names_from = "measure",
    values_from = "mean_per_biom"
  ) %>% 
  mutate(
    total_waste = total_excr_stat + total_uneat_stat,
    total_excr_prop = 100*total_excr_stat/total_waste
  ) %>% 
  select(-total_waste, total_uneat_stat) %>% 
  pivot_longer(
    cols = c(total_excr_stat, total_excr_prop),
    names_to = "measure",
    values_to = "value"
  )

faeces_end %>% 
  ggplot(aes(x = feed_group, y = value, fill = feed_type, group = feed)) +
  geom_boxplot() +
  facet_wrap(facets = vars(measure), scales = "free") +
  prettyplot_300()
```

# Farm locations

For some of the outputs of the model, it makes sense to sum them across a production period and/or calculate their values per unit of biomass. 
```{r biomass-location-globals-farm}

farm_locs <- find_read(output_farm_data_path, "geometry") %>% 
  rename(farm_ID = farm_id) %>% 
  mutate(country = as.factor(country))
```

# Daily results

```{r daily-uneaten-excreted}

daily_results_1 <- cohort_results %>% 
  filter(measure %in% c("total_uneat_stat", "total_excr_stat")) %>% 
  select(-c(mean, sd, mean_biomass, sd_biomass, sd_per_biom)) %>% 
  group_by(feed_group, feed_type, feed, measure, prod_t) %>% 
  reframe(
    mean = mean(mean_per_biom) %>% set_units("g g_fish-1") %>% set_units("g kg_fish-1"),
    sd = sd(mean_per_biom) %>% set_units("g g_fish-1") %>% set_units("g kg_fish-1"),
    min = min(mean_per_biom) %>% set_units("g g_fish-1") %>% set_units("g kg_fish-1"),
    max = max(mean_per_biom) %>% set_units("g g_fish-1") %>% set_units("g kg_fish-1")
  )

daily_results_1 %>% 
  ggplot(aes(x = prod_t, y = mean, colour = feed, group = feed)) +
  geom_line() +
  facet_wrap(facets = vars(measure), scales = "free", nrow = 2) +
  theme_classic()
```

# Spatial results

## Total ends

## Daily mean, min, max

```{r}
space_daily_results_1 <- cohort_results %>% 
  filter(measure %in% c("total_uneat_stat", "total_excr_stat")) %>% 
  select(-c(mean, sd, mean_biomass, sd_biomass, sd_per_biom)) %>% 
  group_by(feed_group, feed_type, feed, measure, farm_ID) %>% 
  reframe(
    mean = mean(mean_per_biom) %>% set_units("g g_fish-1") %>% set_units("g kg_fish-1"),
    sd = sd(mean_per_biom) %>% set_units("g g_fish-1") %>% set_units("g kg_fish-1"),
    min = min(mean_per_biom) %>% set_units("g g_fish-1") %>% set_units("g kg_fish-1"),
    max = max(mean_per_biom) %>% set_units("g g_fish-1") %>% set_units("g kg_fish-1")
  ) %>% 
  merge(farm_locs, by = "farm_ID")

p_bigmap_robinson +
  geom_sf(
    data = space_daily_results_1, 
    aes(colour = drop_units(mean), geometry = geometry), 
    size = 2
  ) +
  coord_sf() +
  scale_color_viridis_c(option = "turbo", breaks = seq(10, 35, 5), limits = c(10,36)) + 
  guides(col = guide_colourbar(
    title = expression("Difference in N inputs (kg/t salmon)"),
    direction = "horizontal", position = "bottom",
    label.position = "bottom", title.position = "top",
    title.vjust = 1, title.hjust = 0.5,
    frame.colour = "black", ticks.colour = "black",ticks.linewidth = 1,
    barheight = 1.5, barwidth = 20,
  )) +
  facet_wrap(facets = vars(feed)) +
  prettyplot_300() +
  theme(
    strip.background = element_blank(), 
    strip.text = element_blank(),
    axis.title = element_blank(),
    legend.position = "bottom"
  )
```

# Old stuff

@@

```{r, eval=F}
#| label: summed-per-biomass-outputs

@@

```{r biomass-location-globals-cohort, eval=F}

@@

```{r summed-per-biomass-outputs-cohort, eval=F}

@@

```{r biomass-produced-comparisons, eval=F}

@@

```{r food-provided-comparison, eval=F}

@@

```{r uneaten-feed-comparisons, eval=F}

@@

@@

```{r, eval=F}
#| label: PLC-mass-inputs-comparison

@@

```{r, eval=F}
#| label: macronutrient-proportion-comparison

@@

```{r, eval=F}
#| label: uneaten-feed-N-comparison

@@

```{r, eval=F}
#| label: excreted-N-comparison

@@

```{r, eval=F}
#| label: total-N-comparison

@@

```{r, eval=F}

@@

### 2025-12-18 index.qmd
Updates to docs

---
title: "Local to Global Mariculture Modelling"
subtitle: "Project Documentation"
author: "Dr Tormey Reimer"
date: today
execute:
  eval: true
  echo: false
  warning: false
  message: false
  cache: true # quarto render index.qmd --cache-refresh
knitr: 
  opts_chunk:
    fig.align: center
    fig.width: 8.5
format:
  html:
    code-fold: true
---

>>>>

---
title: "Local-to-Global Mariculture Modelling"
subtitle: "Project Documentation - Index of files"
author: "Tormey Reimer"
date: today
execute:
  eval: false
---
